SMT-Boosted Security Types for Low-Level MPC

### 2025-01-26 esop25/examples.tex
checkpoint

In the 2-party GMW protocol \cite{evans2018pragmatic}, another garbled
binary circuit protocol, values are encrypted in a manner similar to
BDOZ as described in Section \ref{section-ipj}. In our definition of
GMW we use the convention that shared values $\macgv{\mesg{w}}$ are
identified by strings $w$ and encoded as shares $\mx{w}{1}$ and
$\mx{w}{2}$.  As for YGC, ciphertypes reflect the confidentiality of
GMW input encodings as defined in the $\ttt{encodegmw}$ function in
Figure \ref{fig-gmw}. No programmer annotation is needed given the
syntax of the function body. More interestingly, the $\ttt{andgmw}$
gate definition shows how a programmer hint can express the relevant
confidentiality property of the output share $\mx{z}{2}$ on client
2. The non-trivial equivalence can be verified by SMT once during
verification, and subsequently confidentiality is expressed in the
dependent type of the function (as for $\ttt{encode}$).

@@

Returning to the example of malicious-secure 2-party BDOZ arithmetic
circuits begun in Section \ref{section-ipj}, in Figure \ref{fig-bdozsum} we
define $\ttt{sum}$ and $\ttt{open}$ functions. The latter implements
``secure opening''-- each party sends it's local share of a
global value $\macgv{\mesg{w}}$ along with its MAC to the other party,
which is authenticated via the $\macbdoz{w}$ check (in \ttt{\_open}),
and then each party reconstructs $\macgv{\mesg{w}}$.

The $\ttt{sum}$ function implements an addition gate. Note that this
is done non-interactively-- each party just sums its local shares
of the two values. The pre- and postcondition annotations
on $\ttt{sum}$ express the additive homomorphism associated
with this encryption scheme-- the sum of MACs of the input
shares is a valid MAC for the output share on each client,
which can be checked using the sum of keys of the input shares.

In BDOZ a pre-processing phase is assumed where initial input secrets
are shared along with their associated MACs and keys. This can be
expressed in $\eqspre$ for input secrets $\sx{\ttt{"x"}}{1}$ and
$\sx{\ttt{"y"}}{2}$, for example, which subsume the following
constraints on shares:
{\footnotesize$$
\begin{array}{l}
\mx{\ttt{"xs"}}{2} \eop \sx{\ttt{"x"}}{1} \fminus \rx{\ttt{"x"}}{1} \wedge 
\mx{\ttt{"xs"}}{1} \eop \rx{\ttt{"x"}}{1} \wedge \\
\mx{\ttt{"ys"}}{1} \eop \sx{\ttt{"y"}}{2} \fminus \rx{\ttt{"y"}}{2} \wedge 
\mx{\ttt{"ys"}}{2} \eop \rx{\ttt{"y"}}{2} 
\end{array}
$$}
and the following constraint on keys and MACs for authentication
of $\sx{\ttt{"x"}}{1}$ (and similarly for $\sx{\ttt{"y"}}{2}$):
{\footnotesize$$
\begin{array}{l}
\mx{\ttt{"delta"}}{1} \eop \rx{\ttt{"delta"}}{1} \wedge
\mx{\ttt{"xk"}}{1} \eop \rx{\ttt{"xk"}}{1} \wedge\\
\mx{\ttt{"xm"}}{2} \eop \mx{\ttt{"xk"}}{1} \fplus (\mx{\ttt{"delta"}}{1} * \mx{\ttt{"xs"}}{2})
\end{array}
$$}
Given this, a malicious secure opening of $\sx{\ttt{"x"}}{1} +
\sx{\ttt{"y"}}{2}$ would be obtained as
$\ttt{sum}(\ttt{"z"},\ttt{"x"},\ttt{"y"}); \ttt{open}(\ttt{"z"})$.

A common approach to implementing multiplication gates in a BDOZ
setting is to use \emph{Beaver Triples}. Recall that Beaver triples
are values $a,b,c$ with $a$ and $b$ chosen randomly and $c = a * b$,
unique per multiplication gate, that are secret shared with clients
during pre-processing.  In our encoding we assume the additional
convention that each gate output identifier distinguishes the Beaver
triple, so for example the share of the $a$ value for a gate
$\ttt{"g1"}$ is identified by $\ttt{"g1as"}$, etc., and $\eqspre$
subsumes the following constraints for the $a,b,c$ values of gate
$\ttt{"g1"}$.  {\footnotesize$$
\begin{array}{l}
\mx{\ttt{"g1as"}}{1} \eop \rx{\ttt{"g1as"}}{1}\ \wedge 
\mx{\ttt{"g1bs"}}{1} \eop \rx{\ttt{"g1bs"}}{1}\ \wedge\\
\mx{\ttt{"g1as"}}{2} \eop \rx{\ttt{"g1as"}}{2}\ \wedge 
\mx{\ttt{"g1bs"}}{2} \eop \rx{\ttt{"g1bs"}}{2}\ \wedge\\
\mx{\ttt{"g1cs"}}{1} \eop \\
\qquad ((\mx{\ttt{"g1as"}}{1} \fplus \mx{\ttt{"g1bs"}}{2})\ \ftimes\\
\qquad\phantom{(}(\mx{\ttt{"g1bs"}}{1} \fplus \mx{\ttt{"g1bs"}}{2})) \fminus \rx{\ttt{"g1cs"}}{2}\ \wedge\\
\mx{\ttt{"g1cs"}}{2} \eop \rx{\ttt{"g1cs"}}{2}
\end{array}
$$}

The definition of the $\ttt{mult}$ gate is presented in Figure
\ref{fig-bdozmult}, where we present just client 1's side of the
protocol $\ttt{\_mult1}$ (client 2's side is nearly symmetric but with
a small variation-- refer to
\cite{evans2018pragmatic,10.1007/978-3-030-68869-1_3} for more
details).  We could call this function on input secrets
$\sx{\ttt{"x"}}{1}$ and $\sx{\ttt{"y"}}{2}$ in gate $\ttt{"g1"}$ as
$\ttt{mult}(\ttt{"g1"},\ttt{"x"},\ttt{"y"})$, for example, or embed
this gate internally in a circuit.

As for $\ttt{\_sum}$, the postcondition of the $\ttt{\_mult1}$
function expresses the relevant semi-homomorphic encryption property of
the resulting share, MAC, and key after gate execution-- specifically,
it preserves the BDOZ authentication property. The precondition that
input shares must possess this property is enforced by the two calls
to $\ttt{sum}$ within the body of $\ttt{mult}$ and need not be made
explicit. Finally, the postcondition of $\ttt{mult}$ expresses the
correctness property of the multiplication gate. In any case,
integrity of any circuit constructed from the $\ttt{sum}$ and
$\ttt{mult}$ library functions will require little SMT overhead
due to compositional verification.

>>>>

In the 2-party GMW protocol \cite{evans2018pragmatic}, another garbled
binary circuit protocol, values are encrypted in a manner similar to
BDOZ as described in Section \ref{section-ipj}. In our definition of
GMW we use the convention that shared values $\macgv{\mesg{w}}$ are
identified by strings $w$ and encoded as shares $\mx{w}{1}$ and
$\mx{w}{2}$.  As for YGC, ciphertypes reflect the confidentiality of
GMW input encodings as defined in the $\ttt{encodegmw}$ function in
Figure \ref{fig-gmw}. No programmer annotation is needed given the
syntax of the function body. More interestingly, the $\ttt{andgmw}$
gate definition shows how a programmer hint can express the relevant
confidentiality property of the output share $\mx{z}{2}$ on client 2,
using the $\ttt{as}$ casting. The non-trivial equivalence can be
verified by SMT once during verification, and subsequently
confidentiality is expressed in the dependent type of the function (as
for $\ttt{encode}$).

@@

Returning to the example of malicious-secure 2-party BDOZ arithmetic
circuits begun in Section \ref{section-ipj}, in Figure \ref{fig-bdozsum} we
define $\ttt{sum}$ and $\ttt{open}$ functions. The latter implements
``secure opening''-- each party sends it's local share of a
global value $\macgv{\mesg{w}}$ along with its MAC to the other party,
which is authenticated via the $\macbdoz{w}$ check (in \ttt{\_open}),
and then each party reconstructs $\macgv{\mesg{w}}$. The preconditions
of $\ttt{open}$ specify the authentication requirements.

The $\ttt{sum}$ function implements an addition gate. This is
non-interactive-- each party just sums its local shares
of the two values. The pre- and postcondition annotations
on $\ttt{sum}$ express the additive homomorphism associated
with this encryption scheme-- the sum of MACs of the input
shares is a valid MAC for the output share on each client,
which can be checked using the sum of keys of the input shares.

In BDOZ a pre-processing phase is assumed where initial input secrets
are shared along with their associated MACs and keys. This can be
expressed in $\eqspre$ for input secrets $\sx{\ttt{"x"}}{1}$ and
$\sx{\ttt{"y"}}{2}$, for example, which subsume the following
constraints on shares:
{\footnotesize$$
\begin{array}{l}
\mx{\ttt{"xs"}}{2} \eop \sx{\ttt{"x"}}{1} \fminus \rx{\ttt{"x"}}{1} \wedge 
\mx{\ttt{"xs"}}{1} \eop \rx{\ttt{"x"}}{1} \wedge \\
\mx{\ttt{"ys"}}{1} \eop \sx{\ttt{"y"}}{2} \fminus \rx{\ttt{"y"}}{2} \wedge 
\mx{\ttt{"ys"}}{2} \eop \rx{\ttt{"y"}}{2} 
\end{array}
$$}
and the following constraint on keys and MACs for authentication
of $\sx{\ttt{"x"}}{1}$ (and similarly for $\sx{\ttt{"y"}}{2}$):
{\footnotesize$$
\begin{array}{l}
\mx{\ttt{"delta"}}{1} \eop \rx{\ttt{"delta"}}{1} \wedge
\mx{\ttt{"xk"}}{1} \eop \rx{\ttt{"xk"}}{1} \wedge\\
\mx{\ttt{"xm"}}{2} \eop \mx{\ttt{"xk"}}{1} \fplus (\mx{\ttt{"delta"}}{1} * \mx{\ttt{"xs"}}{2})
\end{array}
$$}
Given these global preconditions, a malicious secure opening of $\sx{\ttt{"x"}}{1} +
\sx{\ttt{"y"}}{2}$ would be obtained as
$\ttt{sum}(\ttt{"z"},\ttt{"x"},\ttt{"y"}); \ttt{open}(\ttt{"z"})$,
which type checks.

A common approach to implementing multiplication gates in a BDOZ
setting is to use \emph{Beaver Triples}. Recall that Beaver triples
are values $a,b,c$ with $a$ and $b$ chosen randomly and $c = a * b$,
unique per multiplication gate, that are secret shared with clients
during pre-processing.  In our encoding we assume the additional
convention that each gate output identifier distinguishes the Beaver
triple, so for example the share of the $a$ value for a gate
$\ttt{"g1"}$ is identified by $\ttt{"g1as"}$, etc.

%, and $\eqspre$
%subsumes the following constraints for the $a,b,c$ values of gate
%$\ttt{"g1"}$.  {\footnotesize$$
%\begin{array}{l}
%\mx{\ttt{"g1as"}}{1} \eop \rx{\ttt{"g1as"}}{1}\ \wedge 
%\mx{\ttt{"g1bs"}}{1} \eop \rx{\ttt{"g1bs"}}{1}\ \wedge\\
%\mx{\ttt{"g1as"}}{2} \eop \rx{\ttt{"g1as"}}{2}\ \wedge 
%\mx{\ttt{"g1bs"}}{2} \eop \rx{\ttt{"g1bs"}}{2}\ \wedge\\
%\mx{\ttt{"g1cs"}}{1} \eop \\
%\qquad ((\mx{\ttt{"g1as"}}{1} \fplus \mx{\ttt{"g1bs"}}{2})\ \ftimes\\
%\qquad\phantom{(}(\mx{\ttt{"g1bs"}}{1} \fplus \mx{\ttt{"g1bs"}}{2})) \fminus \rx{\ttt{"g1cs"}}{2}\ \wedge\\
%\mx{\ttt{"g1cs"}}{2} \eop \rx{\ttt{"g1cs"}}{2}
%\end{array}
%$$}

The definition of the $\ttt{mult}$ gate is presented in Figure
\ref{fig-bdozmult},
%where we present just client 1's side of the
%protocol $\ttt{\_mult1}$ (client 2's side is nearly symmetric but with
%a small variation-- refer to
%\cite{evans2018pragmatic,10.1007/978-3-030-68869-1_3} for more
%details).
%We could call this function on input secrets
%$\sx{\ttt{"x"}}{1}$ and $\sx{\ttt{"y"}}{2}$ in gate $\ttt{"g1"}$ as
%$\ttt{mult}(\ttt{"g1"},\ttt{"x"},\ttt{"y"})$, for example, or embed
%this gate internally in a circuit.
%
As for $\ttt{sum}$, the preconditions of $\ttt{mult}$ express
the expected MAC properties of input shares, as well as the
expected Beaver Triple property, and its postcondition
fexpresses the semi-homomorphic encryption property of
the resulting share, MAC, and key after gate execution-- specifically,
it preserves the BDOZ authentication property. Finally, the
postcondition of $\ttt{mult}$ expresses the
correctness property of the multiplication gate. In any case,
integrity of any circuit constructed from the $\ttt{sum}$ and
$\ttt{mult}$ library functions will require little SMT overhead
due to compositional verification, once their pre- and postconditions
are verified by type checking.
